Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-27 manuscript/ERL_global_C_SI.Rmd
incorporated new changes
#32
#34
#40

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_pt <- read.csv("tables_figures/SI_age_trend_model_summaries.csv", 
                     #colClasses=c("NULL", NA, NA, NA, NA), 
                     #col.names=c("NULL", "Parameter", "Estimate", "SE", "$t_{value}$"), 
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  pack_rows("NEP", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("GPP", 6, 10, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("NPP", 11, 15, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("ANPP", 16, 23, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("ANPP_woody", 24, 28, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("ANPP_stem", 29, 36, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("ANPP_branch", 37, 40, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options =c("repeat_header"), protect_latex = T, font_size = 7)
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_pt <- read.csv("tables_figures/SI_age_trend_model_summaries.csv", 
                     #colClasses=c("NULL", NA, NA, NA, NA), 
                     #col.names=c("NULL", "Parameter", "Estimate", "SE", "$t_{value}$"), 
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  #pack_rows("NEP", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("GPP", 6, 10, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("NPP", 11, 15, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP", 16, 23, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_woody", 24, 28, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_stem", 29, 36, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_branch", 37, 40, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options =c("repeat_header"), protect_latex = T, font_size = 7)
```
